R for Clinical Study Reports and Submission

### 2022-02-12 tlf-baseline.Rmd
fix some minor issues

`text_indent_first` and `test_indent_left` are used to control the indent
space of text. They are helpful when you need to control the white space
of a long phrase "AMERICAN INDIAN OR ALASKA NATIVE"
in the table provide an example.

@@

>>>>

`text_indent_first` and `text_indent_left` are used to control the indent
space of text. They are helpful when you need to control the white space
of a long phrase "AMERICAN INDIAN OR ALASKA NATIVE"
in the table provides an example.

@@

```{r, include=FALSE}
rtf2pdf("tlf/tlf_base.rtf")
```

### 2022-02-12 tlf-overview.Rmd
automate rtf to pdf conversion
source common.R in each Rmd to allow compile individually
fix some minor issues

::: {.rmdnote}
There are other R packages to create TLFs in ASCIII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Reader is encourage to explore other R packages to find the proper tools to fit your purpose. 
:::

@@

There are also books to introduce tidyverse.
We assume the reader have experience in using `tidyverse` in this book.

@@

@@

@@

@@

In `rtf_*()` functions such as `rtf_body()`, `rtf_footnote()`,
the `text_justification` argument is used to align text.
Default is `"c"` for center justification.
To vary text justification by column, use character vector with length of vector equal to
number of columns displayed (e.g., `c("c", "l", "r")`).

@@

@@

>>>>

::: {.rmdnote}
There are other R packages to create TLFs in ASCII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Reader is encouraged to explore other R packages to find the proper tools to fit your purpose. 
:::

@@

There are also books to introduce `tidyverse`.
We assume the reader have experience in using `tidyverse` in this book.

@@

```{r, include=FALSE}
rtf2pdf("tlf/intro-ae1.rtf")
```

@@

```{r, include=FALSE}
rtf2pdf("tlf/intro-ae2.rtf")
```

@@

```{r, include=FALSE}
rtf2pdf("tlf/intro-ae3.rtf")
```

@@

In `rtf_*()` functions such as `rtf_body()`, `rtf_footnote()`,
the `text_justification` argument is used to align text.
Default is `"c"` for center justification.
To vary text justification by column, use character vector with length of vector equals to
number of columns displayed (e.g., `c("c", "l", "r")`).

@@

```{r, include=FALSE}
rtf2pdf("tlf/intro-ae5.rtf")
```

@@

```{r, include=FALSE}
rtf2pdf("tlf/intro-ae7.rtf")
```
